---
title: "Problems and Solutions to Build the Book Advanced R Programming using Rstudio"
author: "dingchendong"
date: "2020/3/18"
output: html_document
---

My computer system is 'windows7'.
```{r eval=FALSE}
git clone https://github.com/hadley/adv-r.git
```
Set working directory temporarily using
```{r eval=FALSE}
setwd("C:/Users/Administrator/mygit/adv-r")
```
Install R Package dependencies using
```{r eval=FALSE}
devtools::install_github("hadley/sloop")
devtools::install_github("hadley/emo")
```
Finally,use'bookdown' package to compile the book.
```{r eval=FALSE}
bookdown::render_book("index.Rmd",output_format = "bookdown::pdf_book")
```
During the building process,i have met some problems,What is shown below is my problems and its solutions.

## Unable to load devtools package

```{r eval=FALSE}
install.packages("devtools")
```

## Quitting from lines 223-235(Introduction.Rmd)

Adding'encoding = "UTF-8"' in line 224 can fix it.
```{r eval=FALSE}
contributors <- read.csv("contributors.csv", stringsAsFactors = FALSE,encoding = "UTF-8")
```

## Quitting from lines 233-234(Perf-measure.Rmd)

```{r eval=FALSE}
install.packages("ggbeeswarm")
```

## 'make' not found
Quitting from lines 77-84(Rcpp.Rmd)

I added `C:\Rtools\bin\` to the path of the environment variable of the computer system, but the error still occurred, so I reinstalled `Rtools` and successfully solved this problem.

## '"xelatex"' not found

According to the yuanyelie's github,i use MiKTeX instead of TinyTex.And choose "Always install missing packages on-the-fly"when MiKTeX let me choose whether missing packages are to be installed.

## Font

I downloaded the font 'andalemono'and'inconsolata'from the internet and install.

After 2 days of intermittent compolation,the book was finally build.
